Statistical Inference for inter-arrival times of extreme events in bursty time series

### 2020-08-01 article_springer/article_springer.Rmd
Small changes according Discussion on 31/7/2020

bibliography: CTRMstats.bib
csl: elsevier-harvard.csl
output:
  rticles::elsevier_article:
    number_sections: true
    fig_caption: yes

@@

We assume a dataset of the form $\{(t_i, x_i), i \in I\}$,
where $t_i$ are timestamps and $x_i$ are magnitudes.
In this article, we focus on modelling the distribution of threshold
*exceedance times* rather than the *exceedances* themselves. For the latter, 
see the POT approach [@smith1984threshold;
@leadbetter1991basis; @davison1990models; @beirlantBook Ch.5.3;
@embrechts2013modelling Ch. 6.5.; @ColesBook Ch.4.].
With the previous section setting the stage, we assume that only the large
magnitudes (aka "shocks") follow a MRP.  The smaller magnitudes are possibly
nuisance data that may be irrelevant with respect to the modelling of extremes
and their waiting times. 
Accordingly, we assume a threshold $\ell$, and discard all
data where $x_i \le \ell$, yielding the thinned dataset
$\{(t^{(l)}_i, x^{(l)}_i), i \in I(\ell)\}$, where $I(\ell) \subseteq I$.

@@

<!-- Suppose the "correct" threshold $\ell_0$ was known, in the sense that  -->
<!-- thresholding at $\ell_0$ would result precisely in an underlying MRP  -->
<!-- $\{(W_i, J_i): i \in I\}$ as defined in Section \ref{sec:CTRE}.  -->
In case we would have data of a MRP $\{(W_i, J_i): i \in I\}$ as defined in Section \ref{sec:CTRE}, we could apply any tail (and scale) estimator such as e.g. Hill's estimator [@hill1975simple] to the $W_i$ and thus infer the distribution of inter-exceedance times. However, in real-world datasets, the MRP assumption is unrealistic for low thresholds. The unknown data generating process is likely to be more complex, with dependencies or mutliple data generating mechanisms at low thresholds, structures that possibly vanish for higher thresholds. Fitting just the IETs means that only the exceedances as well as the times inbetween have to satify the iid assumption.

@@

## Goodness-of-Fit Test

>>>>

bibliography: CTRMstats.bib
csl: elsevier-harvard.csl
output:
  rticles::elsevier_article:
    number_sections: true
    fig_caption: yes
  htlml_document: default

@@

We assume a dataset of the form $\{(t_i, x_i), i \in I\}$,
where $t_i$ are timestamps and $x_i$ are magnitudes.
In this article, we focus on modelling the distribution of threshold
*exceedance times* rather than the *exceedances* themselves. For the latter, 
see the POT approach [@smith1984threshold;
@leadbetter1991basis; @davison1990models; @beirlantBook Ch.5.3;
@embrechts2013modelling Ch. 6.5.; @ColesBook Ch.4.].
With the previous section setting the stage, we assume that only the large
magnitudes (aka "shocks") follow a MRP.  The smaller magnitudes are possibly
nuisance data that may be irrelevant with respect to the modelling of extremes
and their waiting times. 
Accordingly, we assume a threshold $\ell$, and discard all
data where $x_i \le \ell$, yielding the thresholded dataset
$\{(t^{(\ell)}_i, x^{(\ell)}_i), i \in I(\ell)\}$, with $x^{(\ell)}_i=x_i-\ell$, where $I(\ell):=\left\{i: x_i \le \ell \right\} \subseteq I$.

@@

<!-- Suppose the "correct" threshold $\ell_0$ was known, in the sense that  -->
<!-- thresholding at $\ell_0$ would result precisely in an underlying MRP  -->
<!-- $\{(W_i, J_i): i \in I\}$ as defined in Section \ref{sec:CTRE}.  -->
In case we would have data of a MRP $\{(W_i, J_i): i \in I\}$ as defined in Section \ref{sec:CTRE}, we could apply any tail (and scale) estimator such as e.g. Hill's estimator [@hill1975simple] to the $W_i$ and thus infer the distribution of inter-exceedance times. However, in real-world datasets, the MRP assumption is too strong for low thresholds. The unknown data generating process is likely to be more complex, with dependencies or mutliple data generating mechanisms at low thresholds, structures that possibly vanish for higher thresholds. Fitting only the IETs means that the iid assumption applies to exceedances and IETs only.

@@

## Weighing the evidence for non-exponential inter-arrival times
